### 2019-08-19 paper_04_shallow_water/Latex/article.tex
Fix fig 15 in swe paper

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig15}}
\caption{$ \nabla \cdot {\bf u} $ for four different runs. Upper left: WL1, $ Re = 68 $, $ F_f = 0.16 $; Upper right:  { WL3,  $ Re = 203 $, $ F_f = 0.16 $;} Lower left: WL17, $ Re = 68 $, $ F_f = 0.008 $; Lower right: WL18,  $ Re = 199 $, $ F_f = 0.008 $.}
\label{Physical_lap}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig15-eps-converted-to.pdf}}
\caption{Value of $ \nabla \cdot {\bf u} $ for four different runs. $(a)$ WL1,
$ Re = 68 $, $ F_f = 0.16 $; $(b)$ { WL3,  $ Re = 203 $, $ F_f = 0.16 $;} $(c)$
WL17, $ Re = 68 $, $ F_f = 0.008 $; $(d)$ WL18,  $ Re = 199 $, $ F_f = 0.008 $.}
\label{Physical_lap}
\end{figure}
